---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body{
  font-family: 'Times New Roman';
}

h1 {
  color: #000000;
  background-color: #D3D3D3;
  padding: 10px;
  font-weight: bold;
}

h2 {
  color: #000;
  font-weight: bold;
}
```

## Onewa Road Dogs Investigation

This survey is an investigation into the viability of opening a black-haired small-dog grooming business on Onewa Road. To check this I conducted an observational logging survey where I recorded each dog that walked past my house on Monday 31 March between 3pm - 4pm.

The data collected was as follows:

  **1. How many people were walking the dog?**
  
This question simply required a whole numbered input.

  **2. What was the approximate size of the dog?**
  
This question required a rating between 1 Very small, and 5 Very large.

  **3. What colour was the dog?**
  
This question required choosing from a multitude of options. Also included a don't know option in case this wasn't easily answerable.

After this data was collected it was published to a google sheets linked to the google form. This data was then read into R:
```{r}
library(tidyverse)

## Reading in google form data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vS6wYEB-Lu9aLOT9p1mwaJ3XEnD688CgUNE2LXJJbG9Ls9ibDUx2OYGD5PbUydGTfMQt11BvLGRhNOa/pub?output=csv")

```

Next, the column names of the data frame were cleaned up:
```{r}
## Giving appropriate names to each data frame column
latest_data <- logged_data %>%
  rename(People = "1. How many people were walking the dog?",
         Size = "2. What was the approximate size of the dog?",
         Colour = "3. What colour was the dog?")
```

Two summary values were obtained from the data:
```{r}
## Finding a summary value for the average dog size rating
latest_data$Size %>% mean()

paste("The average value for a dog's size rating was", latest_data$Size %>% mean(), ".")

## Finding a range to see the minimum and maximum amount of people walking each dog
latest_data$People %>% range()

paste("The minimum and maximum amount of people walking each dog recorded was", latest_data$People %>% range(), ".")

```


Two bar charts that excellently summarise the data needed for this investigation:
```{r}
## Bar graph to see how common each coloured dog was
ggplot(data = latest_data,
       mapping = aes(x = Colour, fill = as.factor(Colour))) +
  geom_bar() +
  scale_fill_manual(values = c("#e67c73", "#f7cb4d", "#41b375", "#7baaf7", "#b67c8a", "#b2eca7", "#0869af", "#ed553b" ) ) +
  theme_minimal() +
  labs(x = "Colour",
       y = "Number of Observations",
       title = "Number of Each Dog Colour Observed on Onewa Road",
       fill = "")

## Bar graph to see a breakdown in the size of each coloured dog
ggplot(data = latest_data,
       mapping = aes(x = Colour, fill = as.factor(Size))) +
  geom_bar() +
  scale_fill_manual(values = c("#e67c73", "#f7cb4d", "#41b375", "#7baaf7", "#b67c8a", "#b2eca7", "#0869af", "#ed553b" ) ) +
  theme_minimal() +
  labs(x = "Colour",
       y = "Number of Observations",
       title = "Size Breakdown of Each Dog Colour Observed on Onewa Road",
       fill = "")
```




